Three $\approx$40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-27 papers/ms.tex
update ms

\title{
  Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of how stellar clusters evolve.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.  The group contains
  four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the latter three
  systems, which are in other sub-components of the complex (RSG-5 and
  CH-2).  Based on kinematic evidence from Gaia, stellar rotation
  periods from TESS, and spectroscopy, these three systems are also
  $38 \pm 6$ million years old.  Based on the transit shapes and high
  resolution imaging, they are all most
  likely planets (false positive probabilities of $6\times10^{-9}$,
  $5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively).  Kepler-1643 and KOI-7913 are therefore
  the first empirical demonstration that mini-Neptunes with sizes of
  $\approx$2 Earth radii exist at ages of roughly 40 million years.
\end{abstract}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
Broadly speaking these analyses cluster on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of many open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\sim$1\kms, and can be verified to be ``co-eval'' through analyses of
color-absolute magnitude diagrams, stellar rotation periods
\citep{curtis_tess_2019,bouma_2021_ngc2516}, and chemical abundances
\citep{hawkins_2020}.  While there are many implications for our
understanding of star formation and cluster evolution \citep[{\it
e.g.}][]{dinnbier_tidal_2020}, a more immediate consequence is that we
now know the ages of many more stars, including previously known
planet hosts.

%Assuming a constant star formation rate in the Galaxy, $\approx$1\% of
%stars are $\lesssim$10$^8$ years old.  While $\approx$5{,}000
%transiting exoplanets are known (CITE), 11 currently meet this age
%cut.  The discrepancy between the $\approx$50 expected and $\approx$10
%known likely has a contribution from selection effects in planetary
%detection, which include photometric and spectroscopic starspot
%modulation, and the rarity of young stars.

% While detecting planets around young and active stars is challenging,
% so is measuring stellar ages (see CITE Soderblom for a review).  It
% should therefore not be surprising that advances along either
% dimension can yield advances in the census of young transiting
% planets.

@@

In this work, we expand on our previous study of a $38^{+7}_{-6}$
million year old Neptune-sized planet in the Kepler field (Kepler-1627
Ab; \citealt{bouma_kep1627_2022}).  The age of this planet was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
Our analysis of the cluster focused on the immediate spatial and
kinematic vicinity of Kepler-1627~A in order to reliably confirm the
age of the planet.  However it became clear that the $\delta$\ Lyr\
cluster seems to also be part of a much larger group of similarly aged
stars.  This group, which is at a distance of $\approx$300 parsecs
from the Sun, appears to span Cepheus to Hercules (galactic
longitudes, $l$, between 40$^\circ$ and 100$^\circ$), with galactic
latitudes spanning roughly 0 and 20 degrees.  We therefore refer to it
as the Cep-Her complex.  It exhibits significant sub-structure over
its $\approx$250 parsec length, and a detailed analysis that delves
into the memberships, kinematics, and possible origin of the group is
currently being prepared by R.~Kerr and collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we discuss the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc}).

\section{The Cluster}
\label{sec:cluster}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$ pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.
  There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 ($\{ l, b\} \approx \{ 82^\circ,
  6^\circ\}$; $\{ X, Y, Z\} \approx \{60, 330, 50\} $ pc).  The
  local population of candidate young stars around KOI-7368 and
  KOI-7913 is more diffuse -- we call this region ``CH-2''.
  The {\bf interactive figure} enables a few different cuts to be
  shown.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy approximately 200 to 500
parsecs from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$ degrees.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Both of these clusters were known before Gaia, and have reported ages
between $\approx$30 and $\approx$60 million years.  Early empirical
evidence that these two clusters are likely part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{A useful visualization is available online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and tangential velocities with a subsequent manual ``stitching'' step,
and generally supports the idea that there is an overdensity of
$30$--$60\,{\rm Myr}$ old stars in this region of the Galaxy.
\citet{Kerr2021}, in a volume-limited analysis of the Gaia DR2
point-source catalog out to one third of a kiloparsec, identified
three of the nearest sub-populations, dubbed ``Cepheus-Cygnus'',
``Lyra'', and ``Cerberus''.  \citet{Kerr2021} reported ages for each
of these subgroups between 30 and 35 million years.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and a few nearby
sub-populations in this quadrant of the sky share a common origin has
yet to be fully substantiated, and will be the subject of an upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of $10$--$100\,{\rm Myr}$ stars that were observed, we
select candidate Cep-Her members through four steps, the first three
being identical to those described in Section~3 of \citet{Kerr2021}.
We briefly summarize them here.

{\bf TODO RONAN: PLEASE VET ENTIRE SECTION, AND UPDATE WHERE
APPROPRIATE!}.

@@

The second step is to then perform in an unsupervised HDBScan
clustering on the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.
Positions are computed assuming the \texttt{astropy v4.0} coordinate
standard \citep{astropy_2018}, which places the Sun $8122$ pc from the
galactic center, and assumes the solar velocity with respect to the
local standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$ parsecs in physical space,
and $c$ \kms\ in velocity.  The minimum cluster size $N$ is set to 10,
as is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects that are spatially and
kinematically consistent with each of the groups, {\bf IMPROVE
CLARITY at least as close to the 10$^{\rm th}$ nearest
HDBSCAN-identified member in space-velocity coordinates as the most
peripheral HDBSCAN-identified member}.  This third step yields stars
that are spatially and kinematically close to the
photometrically-young stars, but which cannot be identified as young
based on their positions in color versus absolute magnitude.

@@

The fourth and final step was cross-matching our candidate Cep-Her
member list against all known Kepler Objects of Interest, including
known false positives \citep{thompson_planetary_2018}.  This yields 32
matches, of which 5 are ``confirmed'' planets according to the NASA
Exoplanet Archive.  A cursory inspection of the Kepler data validation
summaries and Robovetter classifications for these objects quickly
showed whether they were potentially consistent with being {\it i)}
planets, and {\it ii)} $\lesssim 10^8$ years old population, based on
the presence of rotational modulation at the expected period and
amplitude \citep[{\it e.g.},][Figure~9]{rebull_rotation_2020}.  Four
objects remained after this inspection: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang} shows the positions of the KOIs along
various projections.  Kepler-1643 is near the core RSG-5 population
both spatially and kinematically.  KOI-7368 and KOI-7913 are in a more
diffuse region $\approx$40 parsecs above RSG-5 in $Z$ and $\approx$100
parsecs closer to the Sun in $Y$.  In tangential galactic velocity
space, there may be some kinematic overlap between the region the
latter two KOIs are in, and the main RSG-5 group.

We define two sets of stars in the local vicinity of our objects of
interest, in order to verify whether they are indeed the same age.
For candidate RSG-5 members, we require:
\begin{align}
  45<X/{\rm pc}<75 \nonumber \\
  320<Y/{\rm pc}<350 \nonumber \\
  40<Z/{\rm pc}<70 \nonumber \\
  -4<v_b/{\rm km\,s^{-1}}<-3 \nonumber \\
  4<v_{l^*}/{\rm km\,s^{-1}}<6 \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
	20<X/{\rm pc}<70 \nonumber \\
	230<Y/{\rm pc}<270 \nonumber \\
	75<Z/{\rm pc}<105 \nonumber \\
	-3.5<v_b/{\rm km\,s^{-1}}<-1.5 \nonumber \\
	2<v_{l^*}/{\rm km\,s^{-1}}<6, \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.
% FIXME TODO numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv right now.  Can we do better?
These cuts yield 141 candidate RSG-5 members, and 
37 candidate CH-2 members.
Given the larger volume of the latter group, and the more diffuse base
sample of stars, a major concern is contamination by field stars.
We assess this in the following section.

%Querying the Gaia archive and imposing the cuts suggested by
%\citet[][Appendix B]{GaiaCollaboration2018} on the photometric signal
%to noise ratio, the number of visibility periods used, the
%astrometric $\chi^2$ of the single-source solution, the $G_{\rm
%BP}-G_{\rm RP}$ color excess factor and the parallax precision
%($\varpi/\sigma_\varpi>5$) yields $\approx5.0\times10^6$ sources.
%
%Imposing a thin slice in color-absolute magnitude space around the
%pre-main-sequence of the $\delta$ Lyr cluster's previously
%established $\approx$40 Myr locus, and imposing kinematics cut for
%$-8 < v_b / {\rm km\,s^{-1}} < 0$ and $-15 < v_{l'} / {\rm
%km\,s^{-1}} < 15$, where $l'=l\cos b$, yields $\approx 5.2\times10^3$
%sources.  These objects are all in the range BP-RP 1.5 to 3.2, so
%roughly K5V to M4.5V, or $\approx$0.2 to 0.7 solar masses.  Much more
%manageable, but according to IMF arguments, missing at least a factor
%of two in mass of any clusters.
%
%In XYZ, and in tangential velocity space, these five thousand sources
%are visually clustered in between a few to a dozen groups, depending
%on the characteristic size and velocity scales of interest.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.  The
    bottom left shows gyro (and is a {\bf place-holder since we might
    want to add CH-2 and RSG5}).  The bottom right shows lithium
    (black points are NGC2547 and IC2602 from Randich+18 and probably
    are not believable at the red end; for Kepler-1643 I'm less
    confident, but it might be tied to the ``slow'' rotation period --
    this is why we need RSG5 rotation periods).  Also, we might want
    an H-alpha plot?).
		\label{fig:age}
	}
\end{figure*}

The evidence for the RSG-5 and CH-2 sub-groups at least roughly
sharing the age of the $\delta$\ Lyra\ cluster is shown in
Figure~\ref{fig:age}.

@@

% FIXME FIXME calculate for both!

@@

\section{The Planets}
\label{sec:planet}

@@

\section{Discussion \& Conclusions}
\label{sec:conc}

>>>>

\title{
  Three $\approx$40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of how stellar clusters evolve.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the latter three systems, which are in other
  sub-components of the complex (RSG-5 and CH-2).
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 (in RSG-5) is
  $46^{+9}_{-7}$\,Myr old, while KOI-7368 and KOI-7913 (in CH-2) are
  $36^+{10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, they are
  all most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $5\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  Kepler-1643 and KOI-7913 are therefore the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
Broadly speaking these analyses cluster on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\approx$1\kms, though they can be much higher due to both projection
effects and internal dynamics.  As an extreme example, in the Hyades
the apparent velocities of stars in the tidal tails are expected to
span up to $\pm 40$\kms relative to the cluster center
\citep{jerabkova_800_2021}.  The stars in such diffuse regions can be
verified to be the same age as the core members ({\it i.e.}, co-eval)
through analyses of color-absolute magnitude diagrams, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep[{\it e.g.}][]{dinnbier_tidal_2020}, a more immediate
consequence is that we now know the ages of many more stars, including
previously known planet hosts.

@@

In this work, we expand on our previous study of a $38^{+7}_{-6}$
million year old Neptune-sized planet in the Kepler field (Kepler-1627
Ab; \citealt{bouma_kep1627_2022}).  The age of this planet was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
Our analysis of the cluster focused on the immediate spatial and
kinematic vicinity of Kepler-1627~A in order to confirm the age of the
planet.  However it became clear that the $\delta$\ Lyr\ cluster seems
to also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330 parsecs from the Sun,
appears to span Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes roughly between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we discuss the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc_conc}).

\section{The Cep-Her Complex}
\label{sec:cluster}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 ($\{ l, b\} \approx \{ 82^\circ, 6^\circ\}$;
  $\{ X, Y, Z\} \approx \{60, 330, 50\} $ pc).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2''.
  The {\bf interactive figure} enables a few different cuts to be
  shown.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy approximately 200 to 500
parsecs from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$ degrees.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  They have reported ages
between $\approx$30 and $\approx$60 million years.  Early empirical
evidence that these two clusters could be part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and tangential velocities with a subsequent manual ``stitching'' step,
and generally supports the idea that there is an overdensity of
$\approx$30 and $\approx$60 million year old stars in this region of
the Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the
Gaia DR2 point-source catalog out to one third of a kiloparsec,
identified three of the nearest sub-populations, dubbed
``Cepheus-Cygnus'', ``Lyra'', and ``Cerberus''.  \citet{Kerr2021}
reported ages for each of these subgroups between 30 and 35 million
years.

@@

% {\bf TODO RONAN: PLEASE VET ENTIRE SECTION, AND UPDATE WHERE
% APPROPRIATE!}.

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, and is the subject of the upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of stars that were observed, we select candidate Cep-Her
members through four steps, the first three being identical to those
described in Section~3 of \citet{Kerr2021}.  We briefly summarize them
here.

@@

The second step is to perform in an unsupervised HDBScan
clustering on the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.
Positions are computed assuming the \texttt{astropy v4.0} coordinate
standard \citep{astropy_2018}, which places the Sun $8122$ pc from the
galactic center, and assumes the solar velocity with respect to the
local standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$ parsecs in physical space,
and $c$ \kms\ in velocity.  The minimum cluster size $N$ is set to 10,
as is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBSCAN-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically-young stars, but which cannot be
identified as young based on their positions in color versus absolute
magnitude.

@@

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
The fourth and final step was to cross-match our candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  This yielded 32 matches, of which 18
were known false positives, 7 were designated
``confirmed'', and 8 were designated ``candidates''.  A cursory
inspection of the Kepler data validation summaries and Robovetter
classifications for these objects quickly showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang} shows the positions of the KOIs along
various projections.  Kepler-1643 is near the core RSG-5 population
both spatially and kinematically.  KOI-7368 and KOI-7913 are in a 
diffuse region $\approx$40 parsecs above RSG-5 in $Z$ and $\approx$100
parsecs closer to the Sun in $Y$.  In tangential galactic velocity
space, there may be some kinematic overlap between the region the
latter two KOIs are in, and the main RSG-5 group.

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 70] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -3] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [4, 6] \nonumber
  %45 < X/{\rm pc} < 75 \nonumber \\
  %320 < Y/{\rm pc} < 350 \nonumber \\
  %40 < Z/{\rm pc} < 70 \nonumber \\
  %-4 < v_b/{\rm km\,s^{-1}} < -3 \nonumber \\
  %4 < v_{l^*}/{\rm km\,s^{-1}} < 6 \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
  %20 < X/{\rm pc} < 70 \nonumber \\
  %230 < Y/{\rm pc} < 270 \nonumber \\
  %75 < Z/{\rm pc} < 105 \nonumber \\
  %-3.5 < v_b/{\rm km\,s^{-1}} < -1.5 \nonumber \\
  %2 < v_{l^*}/{\rm km\,s^{-1}} < 6, \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield 141
candidate RSG-5 members, and 37 candidate CH-2 members.  An important
consideration, especially for CH-2, is the
contamination rate by field stars.  We assess this in the following
section.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The stellar groups near KOI-7368, KOI-7913, and Kepler-1643
    are $\approx$40 million years old.} 
    {\it Top row}: 
    Color-absolute magnitude diagram of candidate Cep-Her members, in
    addition to candidate members of the $\delta$~Lyr~cluster
    ($\approx38$\,Myr; \citealt{bouma_kep1627_2022}) and and the Gaia
    EDR3 Catalog of Nearby Stars (gray background).  The left and
    right columns shows stars in RSG-5 and CH-2, respectively.  The
    range of colors displayed is truncated to show whether or not
    candidate members fall on the pre-main-sequence.
    {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr), and Praesepe ($\approx 650$\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.
    Our detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
    {\bf todo: fix zorder markers}.  
		\label{fig:age}
	}
\end{figure*}

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which are designed to
include binaries while omitting instrumental artifacts from for
instance low photometric signal to noise, or a small number of
visibility periods.  We then corrected for extinction using the
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}}
dust maps and the extinction coefficients $k_X\equiv A_X/A_0$from
\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.  This
yielded a mean and standard deviation for the reddening of
$E(B-V)=0.036\pm0.002$ for RSG-5, and $E(B-V)=0.017\pm0.001$
for CH-2.  By way of comparison, in \citet{bouma_kep1627_2022} the
same query for the $\delta$~Lyr cluster yielded
$E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the $\bpmrpo$
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, our membership selection gives stars
that photometrically appear to almost all be on a tight
pre-main-sequence locus.  This implies a false positive rate of at
most a few percent.  By comparison, our control sample (the $\delta$~Lyr
candidates) has a false positive rate of $\approx$12\%, based on the
number of stars that photometrically appear to be more consistent with
the field population than the bulk cluster population.  For CH-2, our
membership selection gives 27 objects in the color range displayed,
and 23 of them appear to be consistent with being on the
pre-main-sequence.  This implies a false positive rate of
$\approx$15\%.

In addition, Figure~\ref{fig:age} shows that the candidate RSG-5 and
CH-2 members overlap with the $\delta$~Lyr cluster, and are therefore
roughly the same age.  To quantify this, we use the empirical method
introduced by \citet[][see their Section~6.3]{gagne_mutau_2020}.  This
idea of the method is to fit the pre-main-sequence loci of a set of
reference clusters, and to then model the locus of the target cluster
as a linear combination of these reference cluster loci.  For our
reference clusters, we used UCL, IC\,2602, and the Pleiades, from the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602\footnote{ Ages for
IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
from 30 to 46\,Myr based on isochronal analyses
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the consequent processing steps were identical to those described
in \citet{bouma_kep1627_2022}.  The mean and standard deviation of the
resulting age posterior are $46^{+9}_{-7}$\,Myr for RSG-5, and
$36^{+10}_{-8}$\,Myr for CH-2.  For comparison, the
this procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The slightly older isochronal age of RSG-5 is
expected given that its locus is slightly bluer and less luminous in
the upper left panel of Figure~\ref{fig:age} relative to the
$\delta$~Lyr cluster.

@@

\section{The Planets}
\label{sec:planets}

@@

\section{Discussion \& Conclusions}
\label{sec:disc_conc}
